Attack-Tolerance in Structured Networks via Multipath Routing

### 2016-02-24 ec-2016/source/paper.tex
Add paper overview.

\begin{bottomstuff}
This work is supported by TODO.

Author's addresses: E.L. Platt and D.M. Romero, School of Information; email: \{elplatt,drom\}@umich.edu.
\end{bottomstuff}

@@

TODO:\\
Fix bibtex encoding\\
Move secrecy section\\
Add ref to unipath butterfly routing\\
Update intro to make significance more clear\\
Clarify identifying fault\\

@@

Paper organization. TODO

>>>>

\begin{bottomstuff}
%This work is supported by TODO.
Author's addresses: E.L. Platt and D.M. Romero, School of Information; email: \{elplatt,drom\}@umich.edu.
\end{bottomstuff}

@@

TODO:\\
Fix bibtex encoding\\
Move secrecy section\\
Update intro to make significance more clear\\
Clarify identifying fault\\

@@

This paper is organized as follows.
Section 2. reviews background and related work.
Section 3. discusses the desired properties of attack-tolerant network
infrastructure.
Section 4. proposes the partial trust model.
Section 5. proposes a general technique for multipath fault tolerance on
structured networks.
Section 6. proposes a specific application of this technique to the butterfly
network topology.
Section 7. discusses these results.
And Section 8. concludes.
